### 2011-07-06 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\documentclass[a4paper,12pt,oneside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage{appendix}

@@

@@

@@

talk about ID, IDREF, ... talk about XML schema keys

@@

TODO FIDAX is cool, but their heuristic might not be the best. It is a IS problem, let's try a multi-purpose solver.

@@

@@

@@

@@

@@

Input -> How long the search for optimum lasts
Time limit -> Quality
Structure of the data -> Which algorithms perform the best
Alpha, Beta -> Quality
Which GLPK -> *
Do I beat FIDAX with random?
Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)

@@

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables

%%% Použité zkratky v diplomové práci, existují-li, včetně jejich vysvětlení.
\chapwithtoc{List of Abbreviations}

@@

%% TODO Appendix - About jInfer

@@

\chapter{jInfer}

>>>>

\documentclass[a4paper,12pt,oneside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage{appendix}
\usepackage{nomencl}

@@

\renewcommand{\nomname}{List of Abbreviations}
\makenomenclature

@@

TODO link to the article mentioning how few XMLs have schemas

@@

\begin{itemize}
	\item XML tree
	\item Element, Attribute
	\item ID, IDREF, IDREFS attribute according to specification
	\item XSD keys (compare them to ID attributes)
	\item Key according to Keys for XML
	\item Attribute mapping
	\item ID set
\end{itemize}

@@

\nomenclature{MIP}{Mixed Integer Problem}

TODO FIDAX is cool, but their heuristic might not be the best. It is a IS problem, let's try a multi-purpose solver. Use GLPK. \nomenclature{GLPK}{GNU Linear Programming Kit}

@@

TODO mention intensification, diversification

@@

TODO explain how this translates to GLPK input

@@

TODO types of data:
\begin{itemize}
	\item Realistic - TODO talk about all that are used
	\item Artificial - random graphs - TODO talk about their generation
\end{itemize}

@@

TODO we will be using jInfer, see \ref{jInfer}.

@@

\begin{itemize}
	\item Input -> How long the search for optimum lasts
	\item Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Which GLPK -> *
	\item Do I beat FIDAX with random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

@@

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

%%% Použité zkratky v diplomové práci, existují-li, včetně jejich vysvětlení.
%\chapwithtoc{List of Abbreviations}

\printnomenclature
\addcontentsline{toc}{chapter}{List of Abbreviations}

@@

@@

\chapter{jInfer}
\label{jInfer}
